---
title: "Capstone EDA"
author: "Ahmed ALRashid"
date: "12/6/2020"
output: html_document
---

## Loading packages 

```{r setup, include=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(Hmisc)
library(RColorBrewer)
library(munsell)
library(janitor)
```


# Loading data set
```{r}

inventory <- read_csv("POs LI 20100419 .csv")
inventory <- clean_names(inventory) # clean the names in the data set
inventory <- subset( inventory, select = -x12 ) # To remove unnecessary column 

```

PO Document = Purchase Order document is a legal document awarded to a supplier/ vendor to supply materials for the a company.  طلب شراء

PO Item = Purchase Order Item. A purchase order may have one or more line items.  بند

Changed On = PO issued or changed

Short Text = short description of an item. وصف البند

Material No = the item catalog number in the company.

Company = the company the PO issued. Do not use ....

Location = the location where the materials will be delivered.

Material/Svcs group = Another scheme numbering system used to organize materials in the catalog.  A Material/Svcs group will have many Materials number.

PO Quantity = Purchase Order item quantity

Order Price Un. = PO Item unit price

Unit Price = the unit price of the line item.

Total LI Value = Total line item price سعر طلب الشراء





```{r}

summary(inventory)

```




```{r}
# Conver currency to a numberic
inventory$unit_price <- as.numeric(gsub('[$,]', '', inventory$unit_price))
inventory$total_li_value <- as.numeric(gsub('[$,]', '', inventory$total_li_value))
```

```{r}
# Changed dates formate to Date so we can use it for our time series analysis
inventory$changed_on <- as.Date(inventory$changed_on,
                                format = "%m/%d/%Y")
typeof(inventory$changed_on)

```



```{r}
glimpse(inventory)
```

```{r}

big_sellers <- inventory %>% 
  group_by(short_text) %>% 
  summarise(n = n()) %>% 
  top_n(10, n)

ggplot(inventory[inventory$short_text %in% big_sellers$short_text,], aes(changed_on, short_text)) +
  geom_point()
```


```{r}
sum(is.na(inventory))
```


```{r}

sample_i <- inventory[sample(nrow(inventory), 1000), ]

```

```{r}

ggplot(sample_i, aes(sample_i$po_document, sample_i$po_quantity)) +
  geom_point(shape = 16, alpha = 0.6,
             size = 3, color = "blue")
```

```{r}

in_top10 <- inventory %>% 
  summarise(inventory, po_quantity) %>% 
  top_n(10)
datatable(in_top10)  
  
```


```{r}

ggplot(sample_i , aes(po_quantity, location)) +
  geom_point(shape = 5, color = "red")

```

```{r}
plot(inventory, aes(inventory$material_no, inventory$po_quantity))
```



















