---
title: "Capstone series analysis"
author: "Ahmed ALRashid"
date: "12/14/2020"
output: html_document
---

## Loading packages 

```{r setup, include=FALSE}

library(tidyverse)
library(janitor)
library(forecast)
library(zoo)
library(xts)
library(lubridate)
library(tidymodels)
library(modeltime)
library(timetk)  

```

# Loading data set
```{r}

inventory <- read_csv("POs LI 20100419 .csv")
inventory <- clean_names(inventory) # clean the names in the data set
inventory <- subset( inventory, select = -x12 ) # To remove unnecessary column 

```

# Convert currency to a numberic
```{r}

inventory$unit_price <- as.numeric(gsub('[$,]', '', inventory$unit_price))
inventory$total_li_value <- as.numeric(gsub('[$,]', '', inventory$total_li_value))
glimpse(inventory)

```


# find out if the po_document or the material_no is unique 
```{r}

length(unique(inventory$po_document))
  

length(unique(inventory$material_no))

```
# as you can see, both po_document and the material_no is not unique because there lenghs are much shorter than the data set


# Adding columns for day, month, year into the data set
```{r}
# I thought I was going to need it for time series 
inventory$day <- format(as.Date(inventory$changed_on), "%d")
inventory$month <- format(as.Date(inventory$changed_on), "%m")
inventory$year <- format(as.Date(inventory$changed_on), "%Y")
```

# adding po_document, po_item and material_no together
```{r}

inventory$po_id <-  paste0(inventory$po_document, inventory$po_item, inventory$material_no)
inventory$po_id <-as.numeric(inventory$po_id)

```

```{r}

# cheack for NAs 
sum(is.na(inventory))

# Delete all rows with NA values
inventory <-  na.omit(inventory)


```


#simplify the data set to a univariate time series with columns, “date” and “value”.
```{r}

inventory <- inventory %>% 
  select(changed_on, po_id) %>%
    set_names(c("date", "value")) 

glimpse(inventory)
```


```{r}

# sorting the data by date
inventory[order(as.Date(inventory$date, format="%Y-%m-%d")),]

```


```{r}

#plot the data
#inventory %>%
 # plot_time_series(date, value, .interactive = FALSE)
```

